---
title: "Details of Traffic Collision - Test Layout"
date: 'Last updated: `r format(Sys.Date(), "%B %d %Y")`'
output:
  html_document:
    number_sections: no
    css: styles/styles.css
    theme: lumen
    toc: no
    toc_float: no
    self_contained: true
    includes:
      after_body: templates/footer.html
always_allow_html: yes
params:
  COLLISION_SERIAL_NO: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

options(scipen = 999)
```

```{r}
library(htmltools)
```

```{r sanity-check}

is_valid_serial_no = (is.numeric(params$COLLISION_SERIAL_NO) &
                          # use isTRUE to escape from logical(0) if COLLISION_SERIAL_NO is NULL
                          isTRUE(params$COLLISION_SERIAL_NO >= 1) & isTRUE(params$COLLISION_SERIAL_NO <= 95821))

if (!is_valid_serial_no) {
  htmltools::p(htmltools::strong("This collision serial number does not exist in the database!"), style = "text-align:center")
}

# Needs to be separated html text above, otherwise HTML text will not be rendered
if (!is_valid_serial_no) {
  knitr::knit_exit()
}

```

```{r}
library(dplyr)
library(tidyr)
library(fst)

library(leaflet)
library(kableExtra)
```

```{r}
## Take data from {hkdatasets}
hk_accidents = fst::read_fst("./data/hk_accidents.fst")
hk_vehicles = fst::read_fst("./data/hk_vehicles.fst")
hk_casualties = fst::read_fst("./data/hk_casualties.fst")
```

```{r}
# color and html properties
LUMEN_THEME_COLOR = "#158cba"
```

```{r}
# 66897 is selected for test
# another for test without long/lat: 79581
hk_accidents_selected = filter(hk_accidents, Serial_No_ == params$COLLISION_SERIAL_NO)

```


## Detail Report of Collision No. `r as.character(params$COLLISION_SERIAL_NO)`

<br>

```{r}
# Fill color palette according to the severity of the accident
fill_palette <- colorFactor(palette = c("#230B4C", "#C03A51", "#F1701E"), domain = c("Fatal", "Serious", "Slight"))

htmltools::HTML(
  paste(
    # Square symbol indicating severity level
    '<div style="height:20px; width:20px; float:left; margin-right:10px; background-color:', fill_palette(hk_accidents_selected[["Severity"]]), '";> </div>',
    
    # Collision severity
    '<h3 style="display: inline !important">', hk_accidents_selected[["Severity"]], ' Collision', '</h3>'
  )
)
```


This collision happened on `r strftime(hk_accidents_selected[["Date_Time"]], "%d %B, %Y (%A), at %H:%S")`. It was a `r hk_accidents_selected[["Severity"]]` collision with `r hk_accidents_selected[["No_of_Casualties_Injured"]]` causalities, involving `r hk_accidents_selected[["No_of_Vehicles_Involved"]]` vehicles. The weather was `r hk_accidents_selected[["Weather"]]` and `r hk_accidents_selected[["Rain"]]`.

The road where collision happened is a `r hk_accidents_selected[["Road_Type"]]` road.

<br>

**Precise location**: `r tools::toTitleCase(tolower(hk_accidents_selected[["Precise_Location"]]))`

```{r, eval=TRUE}
is_valid_loglat = !is.na(hk_accidents_selected$latitude) & !is.na(hk_accidents_selected$longitude)
```

```{r, eval=is_valid_loglat, out.width='100%'}

leaflet(hk_accidents_selected) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addMarkers(~longitude, ~latitude)
```

```{r, eval=!(is_valid_loglat)}
# Show this section if collision does not have long/lat data
p(strong("Detailed location map is not available for this collision."), style = "text-align:center")
```


---

## Details of the collision {.tabset }

Click one of the following tabs to check one specific category details of the collision. Or, click **Show all details** tab to check the full list of details.

```{r}
# classify variables available into separate major types
# require frequent update when dataset changes
vartype_whenwhere = c("Date_Time", "Serial_No_", "District_Council_District", "Street_Name", 
                      "Second_str", "Precise_Location", "Road_Hierarchy", "Structure_Type", "Latitude", "Longitude")

vartype_what = c("Severity" , "Type_of_Collision_with_cycle" , "No_of_Vehicles_Involved" , "No_of_Casualties_Injured",
                 "Hit_and_Run" , "Weather" , "Rain" , "Natural_Light")

vartype_how = c("Vehicle_Movements", "Overtaking", "Road_Type", "Junction_Type", "Within_70m", "Crossing_Type", 
                "Crossing_Control", "Road_Ownership")
```

```{r}
# convert all columns to chr type
row_chr = lapply(hk_accidents_selected, as.character)


# convert back to data frame again, then pivot from single row to single column
hk_accidents_selected_outtable = row_chr %>%
  as.data.frame() %>%
  pivot_longer(cols = everything()) %>%
  # classify by subgroup of variable
  mutate(
      vartype = case_when(
         name %in% vartype_whenwhere ~ "whenwhere",
         name %in% vartype_what ~ "what",
         name %in% vartype_how ~ "how"
         )
  )


# Factor the subgroup to arrange rows easier
arrange_order = c("whenwhere", "what", "how")

hk_accidents_selected_outtable_arrange = hk_accidents_selected_outtable %>%
  mutate(vartype_ft = factor(vartype, levels = arrange_order)) %>%
  arrange(vartype_ft)

table_whenwhere = filter(hk_accidents_selected_outtable_arrange, vartype == "whenwhere") %>% select(name, value)
table_what = filter(hk_accidents_selected_outtable_arrange, vartype == "what") %>% select(name, value)
table_how = filter(hk_accidents_selected_outtable_arrange, vartype == "how") %>% select(name, value)
table_all = filter(hk_accidents_selected_outtable_arrange, !is.na(vartype)) %>% select(name, value)
```


### Date and Place

<br>

Time and detailed location of the collision is shown below.

<br>


```{r}
knitr::kable(
  table_whenwhere,
  col.names	= c("Details", "Description"),
  # Add unique id for further control with css
  table.attr = 'id="accident-subtable"'
) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::column_spec(1, bold = T, border_right = T) %>%
    # change text color and background color of header row
  row_spec(0, color = "#FFFFFF", background = LUMEN_THEME_COLOR)
```

### Severity

<br>

Information about severity and causalities of this collision is shown below.

<br>

```{r}
knitr::kable(
  table_what,
  col.names	= c("Details", "Description"),
  table.attr = 'id="accident-subtable"'
) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::column_spec(1, bold = T, border_right = T) %>%
  # change text color and background color of header row
  row_spec(0, color = "#FFFFFF", background = LUMEN_THEME_COLOR)
```

### How the collision happened

<br>

Information about how the collision happened in shown below.

<br>

```{r}
knitr::kable(
  table_how,
  col.names	= c("Details", "Description"),
  table.attr = 'id="accident-subtable"'
) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::column_spec(1, bold = T, border_right = T) %>%
  # change text color and background color of header row
  row_spec(0, color = "#FFFFFF", background = LUMEN_THEME_COLOR)
```

### Show all details

<br>

Full details of the collision is shown below.

<br>

```{r}
knitr::kable(
  table_all,
  col.names = c("Details", "Description"),
  table.attr = 'id="accident-subtable"') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
  kableExtra::column_spec(1, bold = T, border_right = T) %>%
  # change text color and background color of header row
  row_spec(0, color = "#FFFFFF", background = LUMEN_THEME_COLOR)
```

## {-}

---

## Vehicles involved

```{r}
hk_vehicles_selected = filter(hk_vehicles, Serial_No_ == params$COLLISION_SERIAL_NO)
```

```{r}
SELECTED_VEHICLE_COLUMNS = c("Driver_Age", "Driver_Sex", "Year_of_Manufacture", "Severity_of_Accident", "Vehicle_Class")

hk_vehicles_selected %>%
  select(all_of(SELECTED_VEHICLE_COLUMNS)) %>%
  # do not add thousand separators as year are now in double type
  knitr::kable(caption = "List of vehicles involved") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  # change text color and background color of header row
  row_spec(0, color = "#FFFFFF", background = "#178CBA")
```

## Causalities

```{r}
hk_casualties_selected = filter(hk_casualties, Serial_No_ == params$COLLISION_SERIAL_NO)
```

```{r}
SELECTED_CAUSALTY_COLUMNS = c("Casualty_Age", "Casualty_Sex","Degree_of_Injury", "Role_of_Casualty", "Pedestrian_Action", "Vehicle_Class_of_Driver_or_Pass")

hk_casualties_selected %>%
  select(all_of(SELECTED_CAUSALTY_COLUMNS)) %>%
  # do not add thousand separators as year are now in double type
  knitr::kable(caption = "List of casualties") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  # change text color and background color of header row
  row_spec(0, color = "#FFFFFF", background = "#178CBA")
```

